Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-12 manuscript/manuscript.Rmd

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
clim_id <- rep(c("allClim", "Ppt", "ZPptTemp", "Temp",
                 "Ppt", "ZPptTemp", "Temp", 
                 "Ppt", "ZPptTemp","Temp"), 4)
vital_id <- rep(c("All", "Growth", "Growth", "Growth",
                  "Survival", "Survival", "Survival",
                  "Recruitment", "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(clim_id[i], nrow(tmp))
  tmp$vital <- rep(vital_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")

species <- unique(all_sims$species)
vital_adds <- c("Growth", "Survival", "Recruitment") 
out_controls <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(spp in species){
  tmp <- subset(all_clim_sims, species==spp)
  for(vital in vital_adds){
    tmp$vital <- vital
    out_controls <- rbind(out_controls, tmp)
  }
}
out_controls <- out_controls[2:nrow(out_controls),]

all_noclim_sims <- subset(all_sims, vital!="All")
final <- rbind(out_controls, all_noclim_sims)

equilibrium_cover <- ddply(final, .(species, sim, vital), summarise,
                           eq_cover = median(cover))

mean_cover <- ddply(subset(equilibrium_cover, sim=="allClim"), .(species), summarise,
                    value = median(eq_cover))

myCols2 <- c("#277BA8", "#7ABBBD", "#AED77A")
ggplot(equilibrium_cover, aes(x=sim, y=eq_cover*100, 
                              linetype=vital, group=vital, shape=vital))+
  geom_hline(data=mean_cover, aes(yintercept=value*100), linetype=2, color="grey45")+
  geom_line()+
  geom_point(size=4)+
  facet_grid(species~., scales = "free")+
  scale_linetype_manual(values=c(1,2,3), name="Vital Rate")+
  scale_shape_manual(values=c(19,17,15), name="Vital Rate")+
  ylab("Equilibrium Cover (%)")+
  xlab("Simulation")+
  scale_x_discrete(labels=c("obs", "ppt", "temp", "ppt + tmp"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
setwd("~/Repos/MicroMesoForecast/manuscript")
```

@@

ggplot(ipm_diffs)+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_errorbar(aes(x=species, ymin=lo_cover, ymax=up_cover, group=variable),
                position=dgd, width=0.25, color="grey45")+
  geom_point(aes(x=species, y=med_cover, shape=variable),
             position=dgd, size=5, color="white")+
  geom_point(aes(x=species, y=med_cover, shape=variable),
             position=dgd, size=3)+
#   scale_shape_manual(values = c(19,17), name="Model type")+
  xlab("Climatic change")+
  ylab("Proportional change in percent cover")+
  facet_wrap("type",scales = "free")+
#   scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()

>>>>

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to a 1% increase in precipitation (+ppt), temperature (+temp), or both (+ppt&temp) applied to individual and combined vital rates. For example, the points associated with "G" show the median cover from IPM simulations where a climate perturbation is applied only to the growth regression climate covariates.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, climsim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]

# Rename vital rates with codes
vital_names <- unique(all_sims$vital)
vital_codes <- c("A", "G", "GR", "GS", "R", "S" , "SR") 
vitals <- data.frame(names=vital_names,code=vital_codes)
for(vnow in vital_names){
  ids <- which(all_sims[,"vital"]==vnow)
  idcode <- which(vitals[,"names"]==vnow)
  all_sims[ids,"vital"] <- as.character(vitals[idcode,"code"])
}

# Rep the 'all' simulation for each vital rate for plotting
all_clim_sims <- subset(all_sims, vital=="A")
species <- unique(all_sims$species)
out_controls <- data.frame(time=NA, cover=NA, species=NA, climsim=NA, vital=NA)
for(spp in species){
  tmp <- subset(all_clim_sims, species==spp)
  for(vital in vital_codes){
    tmp$vital <- vital
    out_controls <- rbind(out_controls, tmp)
  }
}
out_controls <- out_controls[2:nrow(out_controls),]

# Combine the datasets
all_noclim_sims <- subset(all_sims, vital!="all")
final <- rbind(out_controls, all_noclim_sims)

# Calculate statistics for plotting
equilibrium_cover <- ddply(final, .(species, climsim, vital), summarise,
                           eq_cover = median(cover))
mean_cover <- ddply(subset(equilibrium_cover, climsim=="all"), .(species), summarise,
                    value = mean(eq_cover))

equilibrium_cover <- subset(equilibrium_cover, vital!="A")
bothid <- which(equilibrium_cover[,"climsim"]=="ppttemp")
equilibrium_cover[bothid,"climsim"] <- "zppttemp"
# myCols2 <- c("#277BA8", "#7ABBBD", "#AED77A")
ggplot(equilibrium_cover, aes(x=climsim, y=eq_cover*100, 
                              shape=vital, group=vital, linetype=vital))+
  geom_hline(data=mean_cover, aes(yintercept=value*100), linetype=2, color="grey45")+
  geom_line()+
  geom_point(size=4)+
  facet_grid(species~., scales = "free")+
  scale_linetype_discrete(name="Vital Rate")+
  scale_shape_discrete(name="Vital Rate")+
  scale_x_discrete(labels=c("baseline", "+ppt", "+temp", "+ppt&temp"))+
  ylab("Equilibrium Cover (%)")+
  xlab("Simulation")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
setwd("~/Repos/MicroMesoForecast/manuscript")
```

@@

# ggplot(ipm_diffs)+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_errorbar(aes(x=species, ymin=lo_cover, ymax=up_cover, group=variable),
#                 position=dgd, width=0.25, color="grey45")+
#   geom_point(aes(x=species, y=med_cover, shape=variable),
#              position=dgd, size=5, color="white")+
#   geom_point(aes(x=species, y=med_cover, shape=variable),
#              position=dgd, size=3)+
# #   scale_shape_manual(values = c(19,17), name="Model type")+
#   xlab("Climatic change")+
#   ylab("Proportional change in percent cover")+
#   facet_wrap("type",scales = "free")+
# #   scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
#   theme_bw()
